---
title: "bv_ccn_demo"
output:
  html_document: default
  pdf_document: default
date: "2025-02-11"
---

```{r}
rm(list=ls())
library(tidyr)
library(dplyr)
library(stringr)
library(magrittr)
library(forcats)
library(dplyr)
library(here)

```
```{r global_options, include=FALSE}
options(scipen=999)
```




```{R}
subjects_with_data = read_csv(file=here::here('data/merged_dataset_with_descriptives.csv')) %>%
  distinct(subject_id)
```



```{r}
demographics <- readRDS(file=here::here("data/bv_ccn_demographics.rds"))
full_demographics <- read.csv(file=here::here("data/bv_ccn_demo.csv"))

full_demographics <- full_demographics %>%
  filter(sid %in% subjects_with_data$subject_id)

```

```{r}
min_age <- min(full_demographics$onboard_age) 
max_age <- max(full_demographics$onboard_age)
avg_age <- mean(full_demographics$onboard_age)*12
sd_age <- sd(full_demographics$onboard_age)

n <- demographics$n
male <- demographics$n_boy/demographics$n*100
female <- demographics$n_girl/demographics$n*100
black <- demographics$n_black/demographics$n*100
asian_pi <- (demographics$n_asian + demographics$n_pacific)/demographics$n*100
white <- demographics$n_white/demographics$n*100
hispanic <- demographics$n_hispanic/demographics$n*100
mixed <- demographics$n_mixed/demographics$n*100
other <- demographics$n_other/demographics$n*100
grad <- full_demographics %>% filter(parent_ed == 6) %>% nrow()
multi_lang <- full_demographics %>% filter(num_lang > 1) %>% nrow()
ca <- full_demographics %>% filter(geo == "CA") %>% nrow()
ne <- full_demographics %>% filter(geo == "NE") %>% nrow()
st <- full_demographics %>% filter(geo == "ST") %>% nrow()
mw <- full_demographics %>% filter(geo == "MW") %>% nrow()
cd <- full_demographics %>% filter(geo == "CD") %>% nrow()
sk <- full_demographics %>% filter(geo == "SK") %>% nrow()
income_info <- full_demographics %>% filter(!is.na(income))
min_income <- min(income_info$income)
max_income <- max(income_info$income)
avg_income <- mean(income_info$income)
sd_income <- sd(income_info$income)
multi_child <- full_demographics %>% filter(house_children > 1) %>% nrow()
single_parent <- full_demographics %>% filter(house_adults == 1) %>% nrow()
multi_caregiver <- full_demographics %>% filter(house_adults > 2) %>% nrow()

```

Thirty-nine families consented to capture home recordings with their infant-toddler (0;5-3;1 years, average age at onboarding = `r avg_age %>% round()` months, SD = `r sd_age %>% round(2)` years, see `Figure~\hyperref[fig:scaling-exp]{1c})`. Families were recruited from a convenience sample of researchers in the field of cognitive development (N=9/39 families) and from local advertisements within the State of California. Some English-speaking and English/Spanish bilingual families (N=19/39) completed parent-report measures of children's language development using the long-forms of the MacArthur-Bates Communicative Development Inventories `\citep{marchman2023, jacksonmaldonado2003}`. See SI for further information on participant consent, detailed demographics, and language questionnaires. 


Our sample is highly educated, with `r grad`/`r n` families having at least one parent with a graduate degree, and with all but one family having at least one parent with a 4-year college degree. `r multi_lang`/`r n` children are exposed to more than one language at home, including the following languages: English, Chinese, Farsi, French, Gujarati, Japanese, Korean, Malayalam, Portuguese, Spanish, Tagalog, Thai, Vietnamese. Geographically, `r ca`/`r n` of families live within California, `r ne`/`r n` live in the Northeastern United States, `r st`/`r n` live in the Southern United States, `r mw`/`r n` live in the Midwestern United States, `r cd`/`r n` live in Canada, and `r sk`/`r n` live in South Korea.

Participating children were `r female %>% round(2)`\% female, `r male %>% round(2)`\% male, `r black %>% round(2)`\% African American/Black, `r asian_pi %>% round(2)`\% Asian American/Pacific Islander, `r white %>% round(2)`\% Caucasian/White, `r hispanic %>% round(2)`\% Hispanic/Latinx, `r mixed %>% round(2)`\% multiracial, `r other %>% round(2)`\% other.

We only have income information for `r income_info %>% nrow()`/`r n` families, as reporting was optional. The average family income of our sample is `r avg_income %>% round(2)` USD (`r min_income`--`r max_income` USD, SD = `r sd_income %>% round(2)` USD). `r multi_child`/`r n` families have more than one child in the household, `r single_parent`/`r n` families live in a single-parent household, and `r multi_caregiver`/`r n` families have more than 2 caregivers living in the household. 

