---
title: "annotation analysis"
output: html_document
date: "2025-2-19"
---

```{r}
library(readr)
library(magrittr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
library(stringr)
library(tidyverse)
```

```{r}

full_transcripts <- read.csv("./ccn_annotated_transcripts.csv") 

# filtering transcripts by speaker for 6-18 month olds

young_adult_transcripts <- full_transcripts %>% filter(annotate_speaker %in% c("FEM","MAL"),age <=18)
young_child_transcripts <- full_transcripts %>% filter(annotate_speaker == "CHI",age <=18)
young_kchild_transcripts <- full_transcripts %>% filter(annotate_speaker == "KCHI",age <=18)

# filtering transcripts by speaker for 18+ month olds

old_adult_transcripts <- full_transcripts %>% filter(annotate_speaker %in% c("FEM","MAL"),age > 18)
old_child_transcripts <- full_transcripts %>% filter(annotate_speaker == "CHI",age > 18)
old_kchild_transcripts <- full_transcripts %>% filter(annotate_speaker == "KCHI",age > 18)

# total and true positive values for the full sample of annotations

full <- full_transcripts %>% filter(!is.na(annotate_speaker)) %>% nrow()
full_tp <- full_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
na <- full_transcripts %>% filter(is.na(annotate_speaker)) %>% nrow()
na_tp <- full_transcripts %>% filter(is.na(annotate_speaker), is.na(speaker)) %>% nrow()

full_acc <- (full_tp + na_tp) / (full + na)

# true positive, actual, and predicted values for adult speakers of 6-18 month olds

ya_tp <- young_adult_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
ya_actual <- young_adult_transcripts %>% nrow()
ya_predicted <- full_transcripts %>% filter(speaker %in% c("FEM","MAL"),age <= 18) %>% nrow()

ya_recall <- ya_tp/ya_predicted
ya_precision <- ya_tp/ya_actual

# true positive, actual, and predicted values for other child speakers of 6-18 month olds

yc_tp <- young_child_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
yc_actual <- young_child_transcripts %>% nrow()
yc_predicted <- full_transcripts %>% filter(speaker == "CHI",age <= 18) %>% nrow

yc_recall <- yc_tp/yc_predicted
yc_precision <- yc_tp/yc_actual

# true positive, actual, and predicted values for key children 6-18 months old

yk_tp <- young_kchild_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
yk_actual <- young_kchild_transcripts %>% nrow()
yk_predicted <- full_transcripts %>% filter(speaker == "KCHI",age <= 18) %>% nrow()

yk_recall <- yk_tp/yk_predicted
yk_precision <- yk_tp/yk_actual

# true positive, actual, and predicted values for adult speakers of 18+ month olds

oa_tp <- old_adult_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
oa_actual <- old_adult_transcripts %>% nrow()
oa_predicted <- full_transcripts %>% filter(speaker %in% c("FEM","MAL"),age > 18) %>% nrow()

oa_recall <- oa_tp/oa_predicted
oa_precision <- oa_tp/oa_actual

# true positive, actual, and predicted values for other child speakers of 18+ month olds

oc_tp <- old_child_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
oc_actual <- old_child_transcripts %>% nrow()
oc_predicted <- full_transcripts %>% filter(speaker == "CHI",age > 18) %>% nrow

oc_recall <- oc_tp/oc_predicted
oc_precision <- oc_tp/oc_actual

# true positive, actual, and predicted values for key children 18+ months old

ok_tp <- old_kchild_transcripts %>% filter(speaker == annotate_speaker) %>% nrow()
ok_actual <- old_kchild_transcripts %>% nrow()
ok_predicted <- full_transcripts %>% filter(speaker == "KCHI",age > 18) %>% nrow()

ok_recall <- ok_tp/ok_predicted
ok_precision <- ok_tp/ok_actual

```

Full Accuracy: `r full_acc`

6-18 Adult Precision: `r ya_precision`

6-18 Adult Recall: `r ya_recall`

6-18 Child Precision: `r yc_precision`

6-18 Child Recall: `r yc_recall`

6-18 Key Child Precision: `r yk_precision`

6-18 Key Child Recall: `r yk_recall`

18+ Adult Precision: `r oa_precision`

18+ Adult Recall: `r oa_recall`

18+ Child Precision: `r oc_precision`

18+ Child Recall: `r oc_recall`

18+ Key Child Precision: `r ok_precision`

18+ Key Child Recall: `r ok_recall`
